---
title: "Test"
author: "Vanessa Machuca"
date: "3/18/2018"
output: pdf_document
---

```{r global_options, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width=5,fig.height=3, fig.align='center')
library(skimr)
library(ggplot2)
library(dplyr)
library(broom)
library(mosaic)
library(readr)
library(lattice)
library(investr)
library(robustbase)
require(gridExtra)
student_por <- read_delim("~/Desktop/MATH158_SLMs/math158_machuspino/student-por.csv", 
    ";", escape_double = FALSE, trim_ws = TRUE)
```


```{r, echo=FALSE}
pairs(~famrel+freetime+goout++health+G3, data=student_por)
```

```{r, echo=FALSE}
int<-lm(G3 ~ Medu*famsup, data=student_por)
summary(int)
```


Time for some backward selection

```{r, echo=FALSE}
drop1(lm(G3~ school + sex + age + address + famsize + Pstatus + Medu + Fedu + Mjob + Fjob + reason + guardian + traveltime + studytime + failures + schoolsup + famsup + paid + activities + nursery + higher + internet + romantic + famrel + freetime + goout + Dalc + Walc + health + absences, data=student_por),test="F")

#delete famsup 

drop1(lm(G3~ school + sex + age + address + famsize + Pstatus + Medu + Fedu + Mjob + Fjob + reason + guardian + traveltime + studytime + failures + schoolsup + paid + activities + nursery + higher + internet + romantic + famrel + freetime + goout + Dalc + Walc + health + absences, data=student_por),test="F")

#delete Medu

drop1(lm(G3~ school + sex + age + address + famsize + Pstatus + Fedu + Mjob + Fjob + reason + guardian + traveltime + studytime + failures + schoolsup + paid + activities + nursery + higher + internet + romantic + famrel + freetime + goout + Dalc + Walc + health + absences, data=student_por),test="F")

#delete traveltime

drop1(lm(G3~ school + sex + age + address + famsize + Pstatus + Fedu + Mjob + Fjob + reason + guardian + studytime + failures + schoolsup + paid + activities + nursery + higher + internet + romantic + famrel + freetime + goout + Dalc + Walc + health + absences, data=student_por),test="F")

#delete Pstatus

drop1(lm(G3~ school + sex + age + address + famsize + Fedu + Mjob + Fjob + reason + guardian + studytime + failures + schoolsup + paid + activities + nursery + higher + internet + romantic + famrel + freetime + goout + Dalc + Walc + health + absences, data=student_por),test="F")

#delete goout 

drop1(lm(G3~ school + sex + age + address + famsize + Fedu + Mjob + Fjob + reason + guardian + studytime + failures + schoolsup + paid + activities + nursery + higher + internet + romantic + famrel + freetime + Dalc + Walc + health + absences, data=student_por),test="F")

#delete reason   

drop1(lm(G3~ school + sex + age + address + famsize + Fedu + Mjob + Fjob + guardian + studytime + failures + schoolsup + paid + activities + nursery + higher + internet + romantic + famrel + freetime + Dalc + Walc + health + absences, data=student_por),test="F")

#delete nursery 

drop1(lm(G3~ school + sex + age + address + famsize + Fedu + Mjob + Fjob + guardian + studytime + failures + schoolsup + paid + activities + higher + internet + romantic + famrel + freetime + Dalc + Walc + health + absences, data=student_por),test="F")

#delete Walc 

drop1(lm(G3~ school + sex + age + address + famsize + Fedu + Mjob + Fjob + guardian + studytime + failures + schoolsup + paid + activities + higher + internet + romantic + famrel + freetime + Dalc + health + absences, data=student_por),test="F")

#delete paid 

drop1(lm(G3~ school + sex + age + address + famsize + Fedu + Mjob + Fjob + guardian + studytime + failures + schoolsup + activities + higher + internet + romantic + famrel + freetime + Dalc + health + absences, data=student_por),test="F")

#delete internet 

drop1(lm(G3~ school + sex + age + address + famsize + Fedu + Mjob + Fjob + guardian + studytime + failures + schoolsup + activities + higher + romantic + famrel + freetime + Dalc + health + absences, data=student_por),test="F")

#delete activities

drop1(lm(G3~ school + sex + age + address + famsize + Fedu + Mjob + Fjob + guardian + studytime + failures + schoolsup + higher + romantic + famrel + freetime + Dalc + health + absences, data=student_por),test="F")

#delete address 

drop1(lm(G3~ school + sex + age + famsize + Fedu + Mjob + Fjob + guardian + studytime + failures + schoolsup + higher + romantic + famrel + freetime + Dalc + health + absences, data=student_por),test="F")

#delete famsize

drop1(lm(G3~ school + sex + age + Fedu + Mjob + Fjob + guardian + studytime + failures + schoolsup + higher + romantic + famrel + freetime + Dalc + health + absences, data=student_por),test="F")

#delete freetime 

drop1(lm(G3~ school + sex + age + Fedu + Mjob + Fjob + guardian + studytime + failures + schoolsup + higher + romantic + famrel + Dalc + health + absences, data=student_por),test="F")

#delete famrel

drop1(lm(G3~ school + sex + age + Fedu + Mjob + Fjob + guardian + studytime + failures + schoolsup + higher + romantic + Dalc + health + absences, data=student_por),test="F")

#delete guardian 

drop1(lm(G3~ school + sex + age + Fedu + Mjob + Fjob + studytime + failures + schoolsup + higher + romantic + Dalc + health + absences, data=student_por),test="F")

#delete Mjob 

drop1(lm(G3~ school + sex + age + Fedu + Fjob + studytime + failures + schoolsup + higher + romantic + Dalc + health + absences, data=student_por),test="F")

#delete Fjob

drop1(lm(G3~ school + sex + age + Fedu + studytime + failures + schoolsup + higher + romantic + Dalc + health + absences, data=student_por),test="F")

#delete absences

drop1(lm(G3~ school + sex + age + Fedu + studytime + failures + schoolsup + higher + romantic + Dalc + health, data=student_por),test="F")

#delete age 

drop1(lm(G3~ school + sex + Fedu + studytime + failures + schoolsup + higher + romantic + Dalc + health, data=student_por),test="F")

#delete romantic

drop1(lm(G3~ school + sex + Fedu + studytime + failures + schoolsup + higher + Dalc + health, data=student_por),test="F")

#delete sex

drop1(lm(G3~ school + Fedu + studytime + failures + schoolsup + higher + Dalc + health, data=student_por),test="F")

#the model above is good at the 0.01 level
#we'll now continue at alpha=0.001

#delete Fedu

drop1(lm(G3~ school + studytime + failures + schoolsup + higher + Dalc + health, data=student_por),test="F")

#delete health

drop1(lm(G3~ school + studytime + failures + schoolsup + higher + Dalc, data=student_por),test="F")

#above is the model for alpha = 0.001

```

This algorithm gave me a 0.01 model with 8 variables: school, Fedu, studytime, failures, schoolsup, higher, Dalc, and health.

studytime - 4 levels

And a 0.001 model with 6 variables: 
school, 
studytime, 
failures, 
schoolsup, 
higher, 
Dalc. 
Add those 3 binary variables for studytime - 9 variables. 
We're going to ask Hardin about how to deal with studytime. 


```{r, echo=FALSE}
pairs(~studytime+failures+Dalc+G3, data=student_por)
```

studytime, schoolsup, Dalc
```{r, echo=FALSE}
int<-lm(G3 ~ failures*schoolsup, data=student_por)
summary(int)
```



studytime-Dalc: 0.152
schoolsup-school: 0.148
school-failures: 0.494
school-higher: 0.101
higher-failures: 0.043
schoolsup-Dalc: 0.0466

studytime-schoolsup: 0.0275
schoolsup-failures: 0.0203

How do we choose which interaction terms to include, if any? Those last two are the most significant. So let's thing about what adding either or both would mean. 


But first, let us recode the variable studytime.

```{r}
student_por_n <- student_por %>% 
mutate(studytime_num = ifelse(studytime == 1, 1, 
ifelse(studytime == 2, 3.5,
ifelse(studytime == 3, 7.5, 12))))
```

```{r}

drop1(lm(G3~ school + sex + age + address + famsize + Pstatus + Medu + Fedu + Mjob + Fjob + reason + guardian + traveltime + studytime + failures + schoolsup + famsup + paid + activities + nursery + higher + internet + romantic + famrel + freetime + goout + Dalc + Walc + health + absences, data=student_por_n),test="F")

#delete famsup

drop1(lm(G3~ school + sex + age + address + famsize + Pstatus + Medu + Fedu + Mjob + Fjob + reason + guardian + traveltime + studytime + failures + schoolsup + paid + activities + nursery + higher + internet + romantic + famrel + freetime + goout + Dalc + Walc + health + absences, data=student_por_n),test="F")

#delete Medu

drop1(lm(G3~ school + sex + age + address + famsize + Pstatus + Fedu + Mjob + Fjob + reason + guardian + traveltime + studytime + failures + schoolsup + paid + activities + nursery + higher + internet + romantic + famrel + freetime + goout + Dalc + Walc + health + absences, data=student_por_n),test="F")

#delete traveltime

drop1(lm(G3~ school + sex + age + address + famsize + Pstatus + Fedu + Mjob + Fjob + reason + guardian + studytime + failures + schoolsup + paid + activities + nursery + higher + internet + romantic + famrel + freetime + goout + Dalc + Walc + health + absences, data=student_por_n),test="F")

#delete Pstatus

drop1(lm(G3~ school + sex + age + address + famsize + Fedu + Mjob + Fjob + reason + guardian + studytime + failures + schoolsup + paid + activities + nursery + higher + internet + romantic + famrel + freetime + goout + Dalc + Walc + health + absences, data=student_por_n),test="F")

#delete goout

drop1(lm(G3~ school + sex + age + address + famsize + Fedu + Mjob + Fjob + reason + guardian + studytime + failures + schoolsup + paid + activities + nursery + higher + internet + romantic + famrel + freetime + Dalc + Walc + health + absences, data=student_por_n),test="F")

#delete reason 

```

Well, we get the same six variables.

```{r}
int<-lm(G3 ~ failures*schoolsup, data=student_por_n)
summary(int)
```

schoolMS-studytime_num: 0.545
schoolMS-failures: 0.494
schoolMS-schoolsup: 0.148
studytime_num-failures: 0.0.23

studytime_num-schoolsup: 0.0276 ***
failures-schoolsup: 0.0203 ***

1=yes and 0=no for schoolsup variable 

Hmm, so the beta for studytime_num-schoolsup is negative, but for failures-schoolsup is 

```{r}

pairs(~G3+failures+studytime_num, data = student_por_n)
```


Many of these variables are quite skewed. Should we omit those which are the most so? 


```{r}
table(student_por_n$Dalc)
```

We will now decide which variables to omit.  We are ommitting Dalc, Famrel.


Let's do some more data exploration:

```{r}
student_por_n %>%
  summary(n())

ggplot(student_por_n,aes(y=G3,x=absences))+geom_point()

```

There are outliers for absences. Let's take them out!

```{r}
student_por_n<- filter(student_por_n, absences < 30)

ggplot(student_por_n,aes(y=G3,x=failures))+geom_point()
```


Let's re-group our four problem variables: failures, Famrel, Dalc, and traveltime:

```{r}
student_por_n<-student_por_n %>%
  mutate(failures=ifelse(failures==2|failures==3,2,failures)) %>%
  mutate(famrel=ifelse(famrel==1|famrel==2,1,ifelse(famrel==3,2,ifelse(famrel==4|famrel==5,3,famrel))))%>%
  mutate(Dalc=ifelse(Dalc==1|Dalc==2,1,ifelse(Dalc==3,2,ifelse(Dalc==4|Dalc==5,3,Dalc))))%>%
  mutate(traveltime=ifelse(traveltime==4,3,traveltime))
```

Let's check to see if all is as it should be, using table. 
Ok, did it. We're good. Moving on.

```{r}
table(student_por_n$age)
```

```{r}
student_por_n<-student_por_n%>%
  mutate(age=ifelse(age==21|age==22,20,age))
```

```{r}
table(student_por_n$studytime_num)
```
Now to build this model!

```{r}
drop1(lm(G3~ school + sex + age + address + famsize + Pstatus + Medu + Fedu + Mjob + Fjob + reason + guardian + traveltime + studytime_num + failures + schoolsup + famsup + paid + activities + nursery + higher + internet + romantic + famrel + freetime + goout + Dalc + Walc + health + absences, data=student_por_n),test="F")

#delete Medu

drop1(lm(G3~ school + sex + age + address + famsize + Pstatus + Fedu + Mjob + Fjob + reason + guardian + traveltime + studytime_num + failures + schoolsup + famsup + paid + activities + nursery + higher + internet + romantic + famrel + freetime + goout + Dalc + Walc + health + absences, data=student_por_n),test="F")

#delete famsup

drop1(lm(G3~ school + sex + age + address + famsize + Pstatus + Fedu + Mjob + Fjob + reason + guardian + traveltime + studytime_num + failures + schoolsup + paid + activities + nursery + higher + internet + romantic + famrel + freetime + goout + Dalc + Walc + health + absences, data=student_por_n),test="F")

#delete Pstatus

drop1(lm(G3~ school + sex + age + address + famsize + Fedu + Mjob + Fjob + reason + guardian + traveltime + studytime_num + failures + schoolsup + paid + activities + nursery + higher + internet + romantic + famrel + freetime + goout + Dalc + Walc + health + absences, data=student_por_n),test="F")

#delete traveltime

drop1(lm(G3~ school + sex + age + address + famsize + Fedu + Mjob + Fjob + reason + guardian + studytime_num + failures + schoolsup + paid + activities + nursery + higher + internet + romantic + famrel + freetime + goout + Dalc + Walc + health + absences, data=student_por_n),test="F")

#delete goout

drop1(lm(G3~ school + sex + age + address + famsize + Fedu + Mjob + Fjob + reason + guardian + studytime_num + failures + schoolsup + paid + activities + nursery + higher + internet + romantic + famrel + freetime + Dalc + Walc + health + absences, data=student_por_n),test="F")

#delete reason

drop1(lm(G3~ school + sex + age + address + famsize + Fedu + Mjob + Fjob + guardian + studytime_num + failures + schoolsup + paid + activities + nursery + higher + internet + romantic + famrel + freetime + Dalc + Walc + health + absences, data=student_por_n),test="F")

#delete internet

drop1(lm(G3~ school + sex + age + address + famsize + Fedu + Mjob + Fjob + guardian + studytime_num + failures + schoolsup + paid + activities + nursery + higher + romantic + famrel + freetime + Dalc + Walc + health + absences, data=student_por_n),test="F")

#delete nursery

drop1(lm(G3~ school + sex + age + address + famsize + Fedu + Mjob + Fjob + guardian + studytime_num + failures + schoolsup + paid + activities + higher + romantic + famrel + freetime + Dalc + Walc + health + absences, data=student_por_n),test="F")

#delete paid

drop1(lm(G3~ school + sex + age + address + famsize + Fedu + Mjob + Fjob + guardian + studytime_num + failures + schoolsup + activities + higher + romantic + famrel + freetime + Dalc + Walc + health + absences, data=student_por_n),test="F")

#delete activities

drop1(lm(G3~ school + sex + age + address + famsize + Fedu + Mjob + Fjob + guardian + studytime_num + failures + schoolsup + higher + romantic + famrel + freetime + Dalc + Walc + health + absences, data=student_por_n),test="F")

#delete address

drop1(lm(G3~ school + sex + age + famsize + Fedu + Mjob + Fjob + guardian + studytime_num + failures + schoolsup + higher + romantic + famrel + freetime + Dalc + Walc + health + absences, data=student_por_n),test="F")

#delete Walc

drop1(lm(G3~ school + sex + age + famsize + Fedu + Mjob + Fjob + guardian + studytime_num + failures + schoolsup + higher + romantic + famrel + freetime + Dalc + health + absences, data=student_por_n),test="F")

#delete famsize

drop1(lm(G3~ school + sex + age + Fedu + Mjob + Fjob + guardian + studytime_num + failures + schoolsup + higher + romantic + famrel + freetime + Dalc + health + absences, data=student_por_n),test="F")

#delete freetime

drop1(lm(G3~ school + sex + age + Fedu + Mjob + Fjob + guardian + studytime_num + failures + schoolsup + higher + romantic + famrel + Dalc + health + absences, data=student_por_n),test="F")

#delete Fjob

drop1(lm(G3~ school + sex + age + Fedu + Mjob + guardian + studytime_num + failures + schoolsup + higher + romantic + famrel + Dalc + health + absences, data=student_por_n),test="F")

#delete Mjob

drop1(lm(G3~ school + sex + age + Fedu + guardian + studytime_num + failures + schoolsup + higher + romantic + famrel + Dalc + health + absences, data=student_por_n),test="F")

#delete guardian

drop1(lm(G3~ school + sex + age + Fedu + studytime_num + failures + schoolsup + higher + romantic + famrel + Dalc + health + absences, data=student_por_n),test="F")

#delete romantic

drop1(lm(G3~ school + sex + age + Fedu + studytime_num + failures + schoolsup + higher + famrel + Dalc + health + absences, data=student_por_n),test="F")

#delete age

drop1(lm(G3~ school + sex + Fedu + studytime_num + failures + schoolsup + higher + famrel + Dalc + health + absences, data=student_por_n),test="F")

#delete absences (whyyy...)

drop1(lm(G3~ school + sex + Fedu + studytime_num + failures + schoolsup + higher + famrel + Dalc + health, data=student_por_n),test="F")

#delete sex

drop1(lm(G3~ school + Fedu + studytime_num + failures + schoolsup + higher + famrel + Dalc + health, data=student_por_n),test="F")

#delete famrel

drop1(lm(G3~ school + Fedu + studytime_num + failures + schoolsup + higher + Dalc + health, data=student_por_n),test="F")

#delete Fedu

drop1(lm(G3~ school + studytime_num + failures + schoolsup + higher + Dalc + health, data=student_por_n),test="F")

#delete health

drop1(lm(G3~ school + studytime_num + failures + schoolsup + higher + Dalc, data=student_por_n),test="F")

#delete Dalc

drop1(lm(G3~ school + studytime_num + failures + schoolsup + higher, data=student_por_n),test="F")

```

At the 0.001 level, we get the following variables in our model:
school
studytime_num
failures
schoolsup
higher

Luis is doing forward selection. I shall now use best subsets to generate another model.

```{r}
student_por_n<-student_por_n1
```

```{r}
require(leaps)
col.best <- regsubsets(G3 ~school + sex + age + address + famsize + Pstatus + Medu + Fedu + Mjob + Fjob + reason + guardian + traveltime + studytime_num + failures + schoolsup + famsup + paid + activities + nursery + higher + internet + romantic + famrel + freetime + goout + Dalc + Walc + health + absences, data=student_por_n, nvmax=10, method="exh") 
col.best.sum <- summary(col.best)

which.min(col.best.sum$cp)
which.max(col.best.sum$adjr2)
which.min(col.best.sum$bic)
```

Model 10 is the best for cp and adjr2.

Model 8 is the best for bic. Let's store them in names. And output the coefficients.


```{r}
best.num.R2 <- which.max(col.best.sum$adjr2) 
best.num.bic <- which.min(col.best.sum$bic) 
best.num.cp <- which.min(col.best.sum$cp)

coef(col.best, best.num.R2)
coef(col.best, best.num.bic)
coef(col.best, best.num.cp)
```


Model 10:
school, sex,Medu,Fjobteacher,failures,schoolsupyes,higheryes,Dalc,health, studytime_num

Model 8:
school,Fedu,failures,schoolsupyes,higheres,Dalc,health,studytime_num

Let us now compare our two models, with the interaction term failers*schoolsup added in.

```{r}
set.seed(42)

for.col <- lm(G3~ school + studytime_num + failures + schoolsup + higher + Walc + schoolsup*failures, data=col.trn)

back.col <- lm(G3~ school + studytime_num + failures + schoolsup + higher + schoolsup*failures, data=col.trn)

pred.col.for <- predict(for.col, newdata=col.tst) 
pred.col.back <- predict(back.col, newdata=col.tst)

sum( (pred.col.for - col.tst$G3)^2)

sum( (pred.col.back - col.tst$G3)^2)
```

Oh no. We need to redo some things let's go.
But first do this

```{r}
student_por_n<-student_por_n %>% filter(age<20) %>%
  filter(absences<30)
```

```{r}
set.seed(47)
col.subset <- sample(c(TRUE, FALSE), nrow(student_por_n), replace=TRUE, prob=c(1/3,2/3))
col.tst <- student_por_n[col.subset,]
col.trn <-student_por_n[!col.subset,]

drop1(lm(G3~ school + sex + age + address + famsize + Pstatus + Medu + Fedu + Mjob + Fjob + reason + guardian + traveltime + studytime_num + failures + schoolsup + famsup + paid + activities + nursery + higher + internet + romantic + famrel + freetime + goout + Dalc + Walc + health + absences, data=col.trn),test="F")

#delete reason

drop1(lm(G3~ school + sex + age + address + famsize + Pstatus + Medu + Fedu + Mjob + Fjob + guardian + traveltime + studytime_num + failures + schoolsup + famsup + paid + activities + nursery + higher + internet + romantic + famrel + freetime + goout + Dalc + Walc + health + absences, data=col.trn),test="F")

#delete goout

drop1(lm(G3~ school + sex + age + address + famsize + Pstatus + Medu + Fedu + Mjob + Fjob + guardian + traveltime + studytime_num + failures + schoolsup + famsup + paid + activities + nursery + higher + internet + romantic + famrel + freetime + Dalc + Walc + health + absences, data=col.trn),test="F")

#delete paid

drop1(lm(G3~ school + sex + age + address + famsize + Pstatus + Medu + Fedu + Mjob + Fjob + guardian + traveltime + studytime_num + failures + schoolsup + famsup + activities + nursery + higher + internet + romantic + famrel + freetime + Dalc + Walc + health + absences, data=col.trn),test="F")

#delete Walc

drop1(lm(G3~ school + sex + age + address + famsize + Pstatus + Medu + Fedu + Mjob + Fjob + guardian + traveltime + studytime_num + failures + schoolsup + famsup + activities + nursery + higher + internet + romantic + famrel + freetime + Dalc + health + absences, data=col.trn),test="F")

#delete Fedu

drop1(lm(G3~ school + sex + age + address + famsize + Pstatus + Medu + Mjob + Fjob + guardian + traveltime + studytime_num + failures + schoolsup + famsup + activities + nursery + higher + internet + romantic + famrel + freetime + Dalc + health + absences, data=col.trn),test="F")

#delete age

drop1(lm(G3~ school + sex + address + famsize + Pstatus + Medu + Mjob + Fjob + guardian + traveltime + studytime_num + failures + schoolsup + famsup + activities + nursery + higher + internet + romantic + famrel + freetime + Dalc + health + absences, data=col.trn),test="F")

#delete Medu

drop1(lm(G3~ school + sex + address + famsize + Pstatus + Mjob + Fjob + guardian + traveltime + studytime_num + failures + schoolsup + famsup + activities + nursery + higher + internet + romantic + famrel + freetime + Dalc + health + absences, data=col.trn),test="F")

#delete Pstatus

drop1(lm(G3~ school + sex + address + famsize + Mjob + Fjob + guardian + traveltime + studytime_num + failures + schoolsup + famsup + activities + nursery + higher + internet + romantic + famrel + freetime + Dalc + health + absences, data=col.trn),test="F")

#delete traveltime

drop1(lm(G3~ school + sex + address + famsize + Mjob + Fjob + guardian + studytime_num + failures + schoolsup + famsup + activities + nursery + higher + internet + romantic + famrel + freetime + Dalc + health + absences, data=col.trn),test="F")

#delete Fjob

drop1(lm(G3~ school + sex + address + famsize + Mjob + guardian + studytime_num + failures + schoolsup + famsup + activities + nursery + higher + internet + romantic + famrel + freetime + Dalc + health + absences, data=col.trn),test="F")

#delete famsize

drop1(lm(G3~ school + sex + address + Mjob + guardian + studytime_num + failures + schoolsup + famsup + activities + nursery + higher + internet + romantic + famrel + freetime + Dalc + health + absences, data=col.trn),test="F")

#famsup

drop1(lm(G3~ school + sex + address + Mjob + guardian + studytime_num + failures + schoolsup + activities + nursery + higher + internet + romantic + famrel + freetime + Dalc + health + absences, data=col.trn),test="F")

#delete guardian

drop1(lm(G3~ school + sex + address + Mjob + studytime_num + failures + schoolsup + activities + nursery + higher + internet + romantic + famrel + freetime + Dalc + health + absences, data=col.trn),test="F")

#delete absences

drop1(lm(G3~ school + sex + address + Mjob + studytime_num + failures + schoolsup + activities + nursery + higher + internet + romantic + famrel + freetime + Dalc + health, data=col.trn),test="F")

#delete freetime

drop1(lm(G3~ school + sex + address + Mjob + studytime_num + failures + schoolsup + activities + nursery + higher + internet + romantic + famrel + Dalc + health, data=col.trn),test="F")

#delete internet

drop1(lm(G3~ school + sex + address + Mjob + studytime_num + failures + schoolsup + activities + nursery + higher + romantic + famrel + Dalc + health, data=col.trn),test="F")

#delete activities

drop1(lm(G3~ school + sex + address + Mjob + studytime_num + failures + schoolsup + nursery + higher + romantic + famrel + Dalc + health, data=col.trn),test="F")

#delete nursery

drop1(lm(G3~ school + sex + address + Mjob + studytime_num + failures + schoolsup + higher + romantic + famrel + Dalc + health, data=col.trn),test="F")

#delete address

drop1(lm(G3~ school + sex + Mjob + studytime_num + failures + schoolsup + higher + romantic + famrel + Dalc + health, data=col.trn),test="F")

#delete romantic

drop1(lm(G3~ school + sex + Mjob + studytime_num + failures + schoolsup + higher + famrel + Dalc + health, data=col.trn),test="F")

#delete schoolsup

drop1(lm(G3~ school + sex + Mjob + studytime_num + failures + higher + famrel + Dalc + health, data=col.trn),test="F")

#delete studytime_num

drop1(lm(G3~ school + sex + Mjob + failures + higher + famrel + Dalc + health, data=col.trn),test="F")
######good at 0.05

#delete famrel

drop1(lm(G3~ school + sex + Mjob + failures + higher + Dalc + health, data=col.trn),test="F")


#delete Dalc

drop1(lm(G3~ school + sex + Mjob + failures + higher + health, data=col.trn),test="F")


#delete Mjob


drop1(lm(G3~ school + sex + failures + higher + health, data=col.trn),test="F")

#delete health

drop1(lm(G3~ school + sex + failures + higher, data=col.trn),test="F")

```


Now to compare the models

```{r}
back.col <- lm(G3~ school + sex + Mjob + failures + higher + famrel + Dalc + health + higher*dalc, data=col.trn)

for.col <- lm(G3~ , data=col.trn)

pred.col.for <- predict(for.col, newdata=col.tst) 
pred.col.back <- predict(back.col, newdata=col.tst)

sum( (pred.col.for - col.tst$G3)^2)

sum( (pred.col.back - col.tst$G3)^2)
```

LOL jk not needed.

Okay, no we're going to generate a nested model by taking out two of the least significant variables. and then use anove to compare them

```{r}
require(car)
vif(fwdselec)
vif(bkwdselec)
```

$$E[Y]=12.27-1.98X_{failures}-1.31X_{schoolMS}-1.10X_{sexM}+1.55X_{higheryes}-0.26X_{health}+0.85X_{Mjobhealth}+0.08X_{Mjobother}+0.70X_{Mjobservices}+1.53X_{Mjobteacher} $$



